\TheTitle

### 2017-07-05 paper/methodology.tex
Methodology: Changing order of subsections
New ordering is :

 - Tasks
 - Commit selection
 - User selection
 - Data Extraction
 - Analysis

In order to determine the effectiveness of the merge-tree model on
comprehension and summarization of git repositories, we conducted a user
study on 12 participants. The user study is a
mixed-methods study, but with more focused on the quantitative aspects.
We chose to use a mixed-methods approach to determine both if the model
is able to improve the time performance and accuracy of the
participants, and if the participants found the merge trees more
enjoyable for the given tasks.

In this section, we describe the describe the methods used in the user
study. This includes the participant criteria, the questions asked, the
method for selecting commits, and a breakdown of the methods used for
analyzing the results.

@@

The questions and tasks are broken down into three groups. The first two
groups are purely quantitative in nature, being conceptual tasks, and
summarization tasks. The third group of questions is to determine the
demographic of our participant.

@@

% TODO: provide the script for question selection
% \lstinputlistings{../selector.py}

>>>>

In order to determine the effectiveness of the merge-tree model on
comprehension and summarization of git repositories, we conducted a user
study on 12 participants. The user study is a mixed-methods study, with
focus on the quantitative aspects in order to capture how effective the
\mt model, if it is, at improving the correctness, accuracy, and time
performance metrics of users when performing summarization tasks. We use
the qualitative questions as a means of determine the preference of the
participants, and what aspects they prefered from each tool.

In this section, we describe the methods used in the user study. This
includes an outline of the tasks, the commit selection, and the user
selection.

@@

The questions and tasks are broken down into four groups. The first two
groups are purely quantitative in nature; we begin with conceptual tasks
to understand whether the DAG is capable of providing users with an
understanding of how a commit is merged into the master branch, and
other commits that it is merged with. We continue with summarization
tasks, to quantitatively understand if the \mt model makes a difference
in summarization tasks. The third portion is purely qualitative, to gain
better understanding of whether participants preferred working with the
\mt model in \tool, or working with the DAG in Gitk, and what aspects
they preferred from each tool. The final group of questions is simply to
gain a better understanding of the demographic of our participants.

%TODO: Look at how to form research questions in LaTeX

We have two primary research questions;
\begin{enumerate}
  \item Is the DAG capable of providing the participants with an
    understanding of the repository events that are related to a commit?
  \item Does the \mt model make a difference in summarization tasks?
\end{enumerate}

@@
